---
title: "ACCE Training - woody plant example"
author: "Georgia Beel"
date: 2020-05-12
output: 
  html_document:
    toc: true
    toc_float: true
    theme: journal 
    highlight: zenburn
---
# Section 1
## Experimenting with different fucntions
### header 3
#### header 4
##### header 5
###### header 6

`back tick should print code font` compared to this

**bold text**

*italics*

***bold italics***

# Section 2
## "Background Information"

### Description
Structure measurements, including height, canopy diameter, and stem diameter, as well as mapped position of individual woody plants

### Abstract
This data product contains the **quality-controlled**, native sampling resolution data from in-situ measurements of live and standing dead woody individuals and shrub groups, from all terrestrial NEON sites with qualifying woody vegetation. The exact measurements collected per individual depend on *growth form*, and these measurements are focused on enabling *biomass and productivity estimation, estimation of shrub volume and biomass, and calibration / validation* of multiple NEON airborne remote-sensing data products. In general, comparatively large individuals that are visible to remote-sensing instruments are mapped, tagged and measured, and other smaller individuals are tagged and measured but not mapped. Smaller individuals may be subsampled according to a nested subplot approach in order to standardize the per plot sampling effort. Structure and mapping data are reported per individual per plot; sampling metadata, such as per growth form sampling area, are reported per plot. For additional details, see the user guide, protocols, and science design listed in the Documentation section in this data product's details webpage.

Latency: The expected time from data and/or sample collection in the field to data publication is as follows, for each of the data tables (in days) in the downloaded data package. See the Data Product User Guide for more information.

vst_apparentindividual: 90

vst_mappingandtagging: 90

vst_perplotperyear: 300

vst_shrubgroup: 90


### Remarks
Queries for this data product will return data from all dates for vst_mappingandtagging (since individuals maybe tagged and mapped many years before a given vegetation structure sampling bout), whereas the vst_perplotperyear, vst_apparentindividual and vst_shrubgroup tables will be subset to data collected during the date range specified. Data are provided in monthly download files; queries including any part of a month will return data from the entire month. In the vst_perplotperyear table, there should be one record per plotID per eventID, and data in this table describe the presence/absence of woody growth forms, as well as the sampling area utilized for each growth form. The vst_mappingandtagging table contains at least one record per individualID, and provides data that are invariant through time, including tagID, taxonID and mapped location (if applicable). Duplicates in vst_mappingandtagging may exist at the individualID level if errors have been corrected after ingest of the original record; in this instance, users are advised to use the most recent record. Records in vst_mappingandtaggingmay be linked to vst_perplotperyear via the plotID and eventID fields. The vst_apparentindividual table contains one record per individualID per eventID, and includes growth form, structure and status data that may be linked to vst_mappingandtagging records via individualID; records may also be linked to vst_perplotperyear via the plotID and eventID fields. For allometric measurements on tree palms and other large, nonwoody individuals, users must download the nst_perindividual table from the related Non-herbaceous perennial vegetation structure data product (DP1.10045.001), and join on the individualID variable. The vst_shrubgroup table contains a minimum of one record per groupID per plotID per eventID; multiple records with the same groupID may exist if a given shrub group is comprised of more than one taxonID. Data provided in the vst_shrubgroup table allow calculation of live and dead volume per taxonID within each shrub group, and records may be linked with vst_perplotperyear via the plotID and eventID fields.

For all tables, duplicates may exist where protocol and/or data entry aberrations have occurred; users should check data carefully for anomalies before joining tables. Taxonomic IDs of species of concern have been 'fuzzed'; see data package readme files for more information.

### Citation
*Please use this citation in your publications. See Data Policy for more info.*
*National Ecological Observatory Network. 2020. Data Product DP1.10098.001, Woody plant vegetation structure. Provisional data downloaded from http://data.neonscience.org on May 12, 2020. Battelle, Boulder, CO, USA NEON. 2020.*


# Section 3
## insert code chunk

```{r chunk name here}
print("Hello world!")
```

echo=FALSE
```{r same as previous, echo=FALSE}
print("Hello world!")
```

### inserting code chunks from another script
When first reading in the code we do not want to display this so, echo=F.
```{r trial, echo=FALSE}
knitr::read_chunk(here::here("analysis.R"))
```
Here we call the first chunk of code by calling its name "analysis-setup"
```{r analysis-setup}

```

You can then go on and on and re-call all the chunks of code with description, like so...

### Prepare data

To prepare the data we exclude rows for which the value of `growth_form` was `NA` or `liana`.

```{r analysis-filter-data}

```



